Fourmile Calibrations and Output

### 2024-07-16 fourmile_outputs_2013edits.Rmd
fixed spatial figs

@@

# gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2011')
# 
# gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2012')
# 
# gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2013')
# 
# gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2014')
# 
# gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2015')
# 
# gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2016')
# 
# gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2017')
# 
# gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2018')
# 
# gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2019')
# 
# gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'grid_2020')
# 
# gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2011')
# 
# gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2012')
# 
# gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2013')
# 
# gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2014')
# 
# gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2015')
# 
# gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2016')
# 
# gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2017')
# 
# gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2018')
# 
# gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2019')
# 
# gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv')) %>%
#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
#   mutate(source = 'statn_2020')

gw <- bind_rows(
  gw_gridall, gw_statnall
  # gw_grid2011, gw_grid2012,
  # gw_grid2013, gw_grid2014,
  # gw_grid2015, gw_grid2016,
  # gw_grid2017, gw_grid2018,
  # gw_grid2019, gw_grid2020,
  # gw_statn2011, gw_statn2012,
  # gw_statn2013, gw_statn2014,
  # gw_statn2015, gw_statn2016,
  # gw_statn2017, gw_statn2018,
  # gw_statn2019, gw_statn2020
) %>%
  mutate(date = mdy(time),
         year = year(date))

@@

<!-- # Join param & RD/RG -->

<!-- ```{r} -->

<!-- join <- gw_maxcumsum %>% -->
<!--   rename(input_data = source) -->

<!-- params1 <- params %>% -->
<!--   dplyr::select(-input_data) %>% -->
<!--   rename(input_data = cal) %>% -->
<!--   dplyr::select(-c(year_missing)) -->

<!-- # -->
<!-- params_weighted1 <- params_weighted %>% -->
<!--   rename(input_data = cal) %>% -->
<!--   pivot_wider(names_from = 'param', -->
<!--               values_from = 'area_weighted_average') %>% -->
<!--   rename_with(~ paste0(., '_weighted'), 2:7) -->

<!-- join <- left_join(join, params1, by = c('input_data')) %>% -->
<!--   pivot_wider(., names_from='param', values_from='value') %>% -->
<!--   pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms') -->

<!-- join <- left_join(join, params_weighted1, by = 'input_data') -->

<!-- write_csv(join, 'flow_params.csv') -->

>>>>

write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_burn_unburn.csv')

@@

gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2011')

gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2012')

gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2013')

gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2014')

gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2015')

gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2016')

gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2017')

gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2018')

gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2019')

gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2020')

gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2011')

gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2012')

gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2013')

gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2014')

gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2015')

gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2016')

gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2017')

gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2018')

gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2019')

gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2020')

gw <- bind_rows(
  gw_gridall, gw_statnall,
  gw_grid2011, gw_grid2012,
  gw_grid2013, gw_grid2014,
  gw_grid2015, gw_grid2016,
  gw_grid2017, gw_grid2018,
  gw_grid2019, gw_grid2020,
  gw_statn2011, gw_statn2012,
  gw_statn2013, gw_statn2014,
  gw_statn2015, gw_statn2016,
  gw_statn2017, gw_statn2018,
  gw_statn2019, gw_statn2020
) %>%
  mutate(date = mdy(time),
         year = year(date))

@@

# Join param & RD/RG

join <- gw_maxcumsum %>%
  rename(input_data = source)

params1 <- params %>%
  dplyr::select(-input_data) %>%
  rename(input_data = cal) %>%
  dplyr::select(-c(year_missing))

#
params_weighted1 <- params_weighted %>%
  mutate(input_data = paste(source, year_missing, sep = "_")) %>% 
  pivot_wider(names_from = 'param',
              values_from = 'area_weighted_average') %>%
  rename_with(~ paste0(., '_weighted'), 4:9) %>%
  dplyr::select(-c(year_missing, source))

join <- left_join(join, params1, by = c('input_data')) %>%
  pivot_wider(., names_from='param', values_from='value') %>%
  pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms')

join <- left_join(join, params_weighted1, by = 'input_data')

write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv')
